FictionEro2 - Affective Impact of Fiction

### 2025-05-12 study2/analysis/2_emotion.qmd
emotions html

**Gender Differences**
- Women rate stimuli on average significantly lower in arousal, enticiment and valence than men, however this difference was not significant for valence.

-Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement. Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.

**Moderators**
- For women, **positive attitudes towards AI** moderated arousal, enticement, and valence ratings, resulting in **more favorable evaluations of AI-generated images**. Negative attitudes moderated valence ratings, leading to less favorable evaluations.

>>>>

**Gender Differences**

- Main manipulation worked for men only - i.e., reality manipulation on the nature of the stimuli on subjective ratings

- Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement. Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.

- Women rate stimuli on average significantly lower in arousal, enticement and valence than men, however this difference was not significant for valence.

**Moderators**

- For women, **positive attitudes towards AI** moderated arousal, enticement, and valence ratings, resulting in **more favorable evaluations of AI-generated images**. Negative attitudes moderated valence ratings, leading to less favorable evaluations.
